---
title: "Earthquake Magnitude Analysis Based on Bayesian statistics"
author:
  - Zhengyu Li (10175000225)
  - Tong Xu (1016500223)
date: "2020/05/30"
output: 
  pdf_document:
    toc: true
    fig_crop: false
    keep_tex: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = TRUE,
	warning = TRUE
)
library(ggplot2)
library(car)
library(forecast)
library(knitr)
library(LearnBayes)
```

\begin{abstract}
The text of your abstract.  150 -- 250 words.This is our abstract.This is our abstract.This is our abstract.This is our abstract.This is our abstract.This is our abstract.This is our abstract.This is our abstract.This is our abstract.This is our abstract.This is our abstract.This is our abstract.This is our abstract.This is our abstract.This is our abstract.This is our abstract.This is our abstract.This is our abstract.This is our abstract.This is our abstract.This is our abstract.This is our abstract.
\end{abstract}

# Introduction {#intro}

Fiji ’s urban area needs to demolish an area of old houses and then rebuild.  Because the Fiji Islands are located on the boundary between the Pacific Plate and the Indian Plate, and are located on the Pacific Rim Volcanic Seismic Belt, the crustal plates collide, squeeze, and deform, making Fiji a country prone to earthquakes.Therefore, when designing a house, the government must simultaneously consider various factors such as budget and earthquake resistance level. Therefore, this article will conduct a statistical analysis of the earthquakes with a magnitude greater than 4.0 in Fiji since 1964. Find the characteristics of the earthquake in the area and provide a reference for the local government's architectural planning.

# Descriptive Statistical Analysis {#sec:1}

We use one of the Harvard PRIM-H project data sets(Dr. John Woodhouse, Dept. of Geophysics, Harvard University). The dataset has 1436 observations on the following five numeric variables: 

$x_1 = depth$ means depth(km).

$x_2 = mag$ means Richter Magnitude, which magnitudes the earthquakes.

$x_3 = stations$ means the number of stations reporting. 

Those events occurred in a cube near Fiji since 1964.

The first part of the observations and the summary of the variables are shown below:

```{r}
data <- quakes
data <- data[,c("depth", "mag", "stations")]
M <- read.csv("./quakes.csv")
head <- head(data)
kable(head, align = 'c', caption = "The First Part of the Observations")
C <- summary(data)
table2 <- cbind(C[1:6., 1], C[1:6, 2], C[1:6, 3])
kable(table2, col.names = c("depth", "mag", "stations"), caption = "Summary of the Dataset" )
```

We can find that the seismal depths(km) ranges from $40 km$ km to $680 km$ with median $247 km$ and mean $311.4 km$, the Richter Magnitudes ranges from $4$ to $6.4$ with median $4.6$ and mean $4.62$, and the number of stations reporting ranges from $10$ to $132$ with median $27$ and mean $33.42$. Next, to make it more vividly, we depict these summary.

```{r}
plot(data)
par(mfrow = c(1,3))
depth <- M$depth
hist(depth,15)
mag <- M$mag
hist(mag,15)
stations <- M$stations
hist(stations,15)
par(mfrow = c(1,3))
boxplot(data$depth, main  = "The Boxplot of Depth(km)");
boxplot(data$mag, main = "The Boxplot of Richer Magnitude");
boxplot(data$stations, main = "The Boxplot of Stations Reporting Number")
```

The above pictures show that $mag$ and $stations$ might be positively correlated. Besides, the magnitudes appears to be normally distributed.

```{r}
#######  BC transformation  ######
lambda <- powerTransform(mag, family = "bcPower")
mag_bc <- BoxCox(mag, lambda = 1.033341)
shapiro.test(mag_bc)
######## Still Unnormal, WHY???  ########
```

From the descriptive analysis, we can not overemphasize the significance of Richter Magnitudes and it deserve further research. We will maily analyze the Richter Magnitudes data in the follwing sections.   





# Method Used in Constructing a Prior

In this part, we analyze the Richter Magnitudes in seismic data via different methods such as noninformative prior and a conjugate joint prior.

## Conventional Noninformative Prior

In the initial stage, we are interested in the population $\mu$ of the magnitudes, but we do not really know the value of the population variace $\sigma^2$. Thus we also treat $\sigma^2$ as an unknown parameter. In the following sections, we will use multiparameter models to obtain the posterior marginal distribution of $\mu$ and $\sigma^2$.

We consider $\mu$ and $\sigma^2$ are independent, thus the conventional noninformative prior is 

$$
\pi(\mu, \sigma^2) \propto \frac{1}{\sigma^2}, -\infty<\mu<\infty,0<\sigma^2<\infty
$$
```{r}
n = length(mag)
ybar = mean(mag)
s2 = var(mag)
```

In the data set, the number of the observations $n = 1436$, the sample mean $\bar{\mathbf{y}} = 4.32$ and the sample variance $s^2 = \frac{1}{n-1}\sum_{i = 1}^{n}(y_i - \bar{y})^2= 0.34$.

The joint posterior density is 

$$
\pi(\mu, \sigma^2|\mathbf{y}) \propto \frac{1}{(\sigma^2)^{n/2 + 1}}e^{-\frac{1}{2\sigma^2}[(n-1)s^2 + n(\bar{y} - \mu)^2]}
$$

Then we use `normchi2post()` in the `LearnBayes` package to compute the logarithm of it.

```{r}
normchi2post(c(ybar, s2), mag)
```

We also use `mycontour()` in `LearnBayes` package to draw the contour lines at $10%$, $1%$, and $0.1%$ of the maximum value of the posterior density.

```{r}
##################################??????????????????????
```


The sampling distribution is
$$
y_1, \dots , y_n \sim N(\mu, \sigma^2), i.i.d.
$$
The marginal posterior density of $\sigma^2$ is 
$$
\sigma^2|\mathbf{y} \sim IG(\frac{n-1}{2}, \frac{(n-1)s^2}{2})
$$
### Method 1: Analytic Formula

The marginal posterior density of $\mu$ is 
$$
\mu|\mathbf{y} \sim t_{n-1}(\mu, s^2/n) = t_{1435}(4.32, 0.000238)
$$
```{r}
round(ybar + qt(c(0.025, 0.975), n - 1) * sqrt(s2/n), 3)
```

The posterior mean $E(\mu|\mathbf{y}) = \bar{y} = 4.32$, and the $95%$ equal tail posterior credible interval of $\mu$ is [4.293, 4.354].

***Compairison with frequentist analysis***. We then compare our bayesian model with frequentist analysis.

```{r}
t.test(mag)
```

We find that the frequentist $95%$ percent confidence interval is also [4.293, 4.354], matching our previous analysis.

### Method 2: Direct Simulation

In this section, we will base on the direct simulation from the posterior distribution of $\mu$.

```{r}
# rt() generates random deviates
post1.mu <- ybar + rt(10000, n-1) * sqrt(s2/n)
mean(post1.mu)
quantile(post1.mu, prob = c(0.025, 0.975))
```

The result is similar to the conclusion based on the analytic formula for the posterior distribution. 

***The efficiency of direct simulation***. We can see the efficiency of direct simulation by imposing the posterior density of $\mu$ on the histogram of the posterior sample.

```{r}
hist(post1.mu, freq = F, cex.lab = 2, cex.axis = 1.5)
rug(jitter(post1.mu))
gt <- function(x){
  dt((x - ybar)/sqrt(s2/n), n-1)/sqrt(s2/n)
}
curve(gt(x), add = T, col = "red")
```


### Method 3:Indirect Simulation

In this section, we will base on the indirect simulation from the joint posterior distribution of both $\mu$ and $\sigma^2$. We fistly simulate $\sigma^2$, then simulate $\mu | \sigma^2$, and repeat the precess by `normpostsim()` in `LearnBayes` package.

```{r eval=FALSE, include=FALSE}
########## 
d <- normpostsim(mag, n = 10000)
mean(d$mu)
quantile(d$mu, prob = c(.025, .975))
```

```{r eval=FALSE, include=FALSE}
hist(post2.mu, freq = F, cex.lab = 2, cex.axis = 1.5)
rug(jitter(post1.mu))
gt <- function(x){
  dt((x - ybar)/sqrt(s2/n), n-1)/sqrt(s2/n)
}
curve(gt(x), add = T, col = "red")
```

```{r}
### mycontour
```

 

## A Conjugate Joint Prior

# MCMC Method

## Noninformative Prior with MCMC

## Conjugate Joint Prior with MCMC

# Hierarchical Model

# Results

# Conclusion

# References

# Appendix: Code 


